What covert verbal actions tell us about the interplay between language, action, and perception

### 2021-04-13 manuscript.tex
minor figures updates

In this perspective, we explore some of the theoretical and experimental consequences of considering covert verbal actions (e.g., covert speech, covert typing) as inhibited verbal actions... We explore two main themes. First, how is produced...

@@

\subsection{Sensory content: Simulation vs. association}

@@

To be even more precise, \cite{ridderinkhof_dont_2014} described the concept of response inhibition on three continuous dimensions (intentionality, premeditation, specificity). Inhibition can be employed with more or less intentionality (intentional versus reactive inhibition), planned ahead or employed in the moment (early versus late inhibition), and more or less specifically (global inhibition versus effector-specific or action-specific inhibition). More detailed categorisation of inhibitory mechanisms can occur in this three-dimensional space but for the current purpose it is sufficient to say that we are interested (purportedly) in an intentional (we know we want to produce motor imagery rather than overt execution) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition...

@@

\cite{watson_psychology_1919} suggested that thought (i.e., covert speech, in his terminology) was rooted in (overt) speech, that is, that it matured from overt speech... Vygotsky idea of speech internalisation and development of inhibition... Vygotsky observed, as Piaget did before, that egocentric or "private" speech tend to be internalised during child development... \cite{fernyhough_alien_2004} extended this model... What if speech internalisation was related to the development of inhibitory abilities?

These ideas could be assessed experimentally in several ways. First, the relation between speech internalisation and inhibitory abilities could be assessed during development at the critical ages (i.e., between 6 and 8 years). We would expect the ability to imagine actions and speech specifically to be positively correlated with inhibitory skills at at this stage. Second, the inhibitory perspective presented here could be causally assessed by manipulation the inhibitory network preventing execution during motor imagery. For instance, using TMS, can we brake these inhibitory mechanisms and "force" execution during motor imagery... \citep{angelini_motor_2015, angelini_proactive_2016}... Third and finally, inhibition "deficits" in Tourette syndrom...

@@

Summary of the main proposition (i.e., considering covert verbal actions as inhibited verbal actions) and its consequences on the relation between perception and action, theoretical and experimental perspectives.

@@

\begin{figure}[ht] % float was h! initially
\begin{center}
\includegraphics[width=10cm]{figures/logo1} % This is a *.eps file
\end{center}
\caption{Prediction-by-simulation and prediction-by-association mechanisms... FIGURE IN PROGRESS.}\label{fig:1}
\end{figure}

\begin{figure}[ht] % float was h! initially
\begin{center}
\includegraphics[width=10cm]{figures/inhibitory_triangle.png} % This is a *.eps file
\end{center}
\caption{Inhibitory triangle... FIGURE IN PROGRESS.}\label{fig:2}
\end{figure}

>>>>

In this perspective, we explore some of the theoretical and experimental consequences of considering covert verbal actions (e.g., covert speech, covert typing) as inhibited verbal actions... We explore two main themes. First, how is produced... Second... by joining together results from motor imagery, motor inhibition, and covert speech research, we highlight some...

@@

\subsection{Sensory content: prediction-by-simulation vs. prediction-by-association}

@@

To be even more precise, \cite{ridderinkhof_dont_2014} described the concept of response inhibition on three continuous dimensions (intentionality, premeditation, specificity). Inhibition can be employed with more or less intentionality (intentional vs. reactive inhibition), planned ahead or employed in the moment (early vs. late inhibition), and more or less specifically (global inhibition versus effector-specific or action-specific inhibition). More detailed categorisation of inhibitory mechanisms can occur in this three-dimensional space but for the current purpose it is sufficient to say that we are interested (purportedly) in an intentional (we know we want to produce motor imagery rather than overt execution) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition...

@@

\cite{watson_psychology_1919} suggested that thought (i.e., covert speech, in his terminology) was rooted in (overt) speech, that is, that it matured from overt speech... \cite{vygotsky_thought_1934} idea of speech internalisation and development of inhibition... Vygotsky observed, as Piaget did before, that egocentric or "private" speech tend to be internalised during child development... \cite{fernyhough_alien_2004} extended this model... What if speech internalisation was related to the development of inhibitory abilities?

These ideas could be assessed experimentally in several ways. First, the relation between speech internalisation and inhibitory abilities could be assessed during development at the critical ages (i.e., between 6 and 8 years). We would expect the ability to imagine actions and speech specifically to be positively correlated with inhibitory skills at at this stage...  \cite{wang_relationship_2021} provided correlational evidence that motor imagery and motor inhibition performance improve together between 7 and 11 years old, and that these two abilities correlated at 7 years old, but not later... Second, the inhibitory perspective presented here could be causally assessed by manipulation the inhibitory network preventing execution during motor imagery. For instance, using TMS, can we brake these inhibitory mechanisms and "force" execution during motor imagery... \citep{angelini_motor_2015, angelini_proactive_2016}... Third and finally, inhibition "deficits" in Tourette syndrom...

@@

% Summary of the main proposition (i.e., considering covert verbal actions as inhibited verbal actions) and its consequences on the relation between perception and action, theoretical and experimental perspectives...

To sum up, we explored the analogy between covert verbal actions such as covert speech and other forms of motor imagery. This led us to a discussion of two main themes, that is, the question of how the sensory content of motor imagery is produced, and the question of how is it possible for motor imagery not to lead to motor execution. To sketch an answer to these questions, we connected results from the distinct motor imagery, the inner speech, the motor inhibition literature...

We suggested that (section 1 propositions)... and (section 2 propositions)... Taken together, these propositions pave the way for many lines of research that should...

@@

\begin{figure}[ht] % float was h! initially
\begin{center}
\includegraphics[width=0.75\textwidth]{figures/association_simulation.png} % This is a *.eps file
\end{center}
\caption{The balance (weighing) of the prediction-by-simulation (in blue) and prediction-by-association (in orange) mechanisms during covert verbal actions depends on both internal (individual) and external (situational) characteristics that jointly determine the computation cost of each option... FIGURE IN PROGRESS.}\label{fig:1}
\end{figure}

\begin{figure}[ht] % float was h! initially
\begin{center}
\includegraphics[width=0.75\textwidth]{figures/inhibitory_triangle.png} % This is a *.eps file
\end{center}
\caption{Neural implementation of the inhibitory mechanisms responsible for proactive inhibition. The cerebral complex formed by the preSMA, the rIFC and the STN is known as the inhibitory triangle may be responsible for braking motor commands... FIGURE IN PROGRESS.}\label{fig:2}
\end{figure}
